Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}

### 2019-04-13 manuscript.Rnw
incorporate changes from James

{\abstract Conjoint analysis is an increasingly prominent tool for studying political preferences. The method powerfully disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as political candidates or public policies. Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs), which measure the degree to which a given value of a conjoint profile feature increases or decreases respondents' support for the overall profile relative to a baseline, averaging across all respondents and all other profile features. While the AMCE has a clear causal interpretation (about the \textit{effect} of features), most published conjoint analyses also use AMCEs to simply describe \textit{levels} of preferences or favorability, often including comparisons of AMCEs between subgroups of respondents. We show how this descriptive use of conditional AMCEs can be substantially misleading about the degree of agreement or disagreement between subgroups due the simple property that regression interactions are sensitive to the reference category used in the analysis. This leads to inferences about subgroup differences in preferences that have arbitrary sign, size, and significance. We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation using two quantities of interest: the marginal mean and the omnibus F-test. Amidst the rapidly accelerating use of conjoint analyses, we highlight common pitfalls and offer advice for best practice in the analysis and presentation of conjoint experiments.}

@@

Amidst the dramatically increased use of experiments within political science \citep{Druckmanetal2006, Mutz2011}, conjoint experimental designs have recently become a prominent methodological tool in political science. While survey experiments have traditionally examined just one or two factors that might shape outcomes \citep[see, for reviews,][]{GainesKuklinskiQuirk2007, Sniderman2011}, conjoint designs allow researchers to study the independent effects on preferences of many features of complex, multidimensional objects such as political candidates \citep{Campbelletal2016, TeeleKallaRosenbluth2018}, immigrant admissions \citep{HainmuellerHopkins2015, BansakHainmuellerHangartner2016, WrightLevyCitrin2016}, or public policies \citep{GallegoMarx2017, Hankinson2018}. Factorial designs of this sort have a long history but the driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a small-sample, fully randomized conjoint design and an associated analytic approach that emphasizes a single quantity of interest: namely, the average marginal component effect (AMCE). By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit or implicit confounding between features of these objects, giving the AMCE a clear causal interpretation: the degree to which a given value of a feature increases or decreases respondents' favorability toward a packaged conjoint profile relative to a baseline.

While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs not only for \textit{causal} purposes (interpreting AMCEs as effect sizes), but also for \textit{descriptive} purposes: that is, to map levels of favorability toward a multidimensional object across its various features.\footnote{See \citet{Shmueli2010} for an elaboration on the distinctions between explanatory (causal) modelling, descriptive modelling, and predictive modelling.} In this sense, conjoints are often applied like list experiments, using randomization to measure a sample's preferences over something difficult to measure with direct questioning. A positive (negative) AMCE for a given feature can be read as a descriptive measure of high (low) favorability toward profiles with that feature. Though the quantity is causal, it is often read descriptively.

This is particularly the case when researchers engage in subgroup analyses of conjoint experiments in search of preference heterogeneity. Such exercises are an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017, EgamiImai2018}. For example, \citet{HainmuellerHopkinsYamamoto2014} perform a subgroup analysis on their original immigration experiment in which they perform a median split on a measure of ethnocentrism and then compare AMCEs for the two subgroups. Similarly, \citet{BansakHainmuellerHangartner2016} compare preferences toward immigrants across number of binary respondent characteristics: age, education, left-right ideology, and income. In a different domain, \citet{BallardRosaMartinScheve2016} compare preferences over tax policies across a number of subgroups defined by demographics and political orientations. \citet{BechtelScheve2013} compare AMCEs on climate agreements across four different countries, and across subgroups of respondents. \citet{TeeleKallaRosenbluth2018} compare AMCEs for features of male and female political candidates among male and female respondents. Most of these comparisons are visual or informal. But some involve explicit estimation of the subgroup difference, such as when \citet{KirklandCoppock2017} compare conditional AMCEs across hypothetical partisan and nonpartisan elections. Interpretation of subgroup AMCEs thus involves an implied quantity of interest: the \textit{difference} between two conditional AMCEs.

What is not necessarily obvious in such analyses is that differences-in-preferences (that is to say, the difference in degree of favorability toward profiles containing a given feature) are not directly reflected in subgroup differences-in-AMCEs. A difference in effect sizes is distinct from a difference in the preferences so affected. We show that a difference in two (or more) subgroups' favorability toward a conojoint feature --- like a difference in willingness to support a Syrian immigrant between high and low ethnocentrism respondents --- is only reflected in the difference-in-AMCEs in very rare circumstances. As such, no information about the similarity of the subgroups' preferences is provided by comparisons of subgroup AMCEs, yet such comparisons are commonly made in practice.

As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well but where preferences between subgroups diverge in the reference category, the difference-in-AMCEs is a misleading representation of underlying patterns of favorability. Given most published conjoint studies appear to report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment, difference-in-AMCEs should not be assumed to be interpretable as differences in subgroup preferences.\footnote{For example, in a comparison of subgroup effects for Democrats and Republicans, Republicans might display a smaller effect because their preferences in the reference category are already very positive, such that a large positive effect for Democrats occurs despite Democrats being less supportive than Republicans in either experimental condition.} The root of this error is likely familiar to many researchers: it is simply a matter of regression specification for models involving interactions between categorical regressors. \citet{EgamiImai2018}, for example, provide an extensive discussion of the implications of this property for interpreting causal interactions between randomized features of conjoint profiles. The state of the published literature would suggest the problem remains non-obvious when applied to descriptive analysis of subgroups in conjoint designs.

In what follows, we demonstrate the challenges of conjoint analysis and remind readers of how reference category choice for profile features creates problems for comparing conditional AMCEs across respondent subgroups. We show how the use of an arbitrary reference category means the size, direction, and statistical significance of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features; reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar. We demonstrate this with examples drawn from the published political science literature (namely experiments by \citealt{HainmuellerHopkinsYamamoto2014, BechtelScheve2013, TeeleKallaRosenbluth2018}). The paper then provides suggestions for improved conjoint reporting and interpretation based around two quantities of interest drawn from the factorial experimentation literature: (a) unadjusted marginal means, a quantity measuring favorability toward a given feature, and (b) an omnibus F-test, measuring differences therein. Software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment --- is demonstrated throughout. We conclude with advice for best practices in the analysis and presentation of conjoint results.

@@

Analytically, a fully randomized conjoint design without constraints between profile features is simply a full-factorial experiment (with some cells possibly, albeit randomly, left unobserved). All quantities of interest relevant to the analysis of conjoint designs therefore derive from combinations of cell means, marginal means, and the grand mean, as in the traditional analysis of factorial experiments. In a forced choice conjoint design, the \textit{grand mean} is by definition 0.5 (i.e., 50\% of all profiles shown are chosen and 50\% are not chosen). \textit{Cell means} are the mean outcome for each particular combination of feature levels. In the full-factorial design discussed by \citet{HainmuellerHopkinsYamamoto2014} and now widely used in political science, many or perhaps most cell means are unobserved. For example, in their candidate choice experiment, there are $2*6*6*6*2*6*6*6 = 186,624$ cell means but only 3,466 observations so about 98\% of cell means are unobserved. While this would be problematic for attempting to infer pairwise comparisons between cells, conjoint analysts mostly focus on the marginal effects of each feature rather than more complex interactions. Appendix \ref{app:quantities} provides detailed notation and elaborations of these definitions of quantities of interest.

In fully randomized designs, the average marginal component effects (AMCEs) are simply marginal effects of changing one feature level to another, all else constant. AMCEs therefore depend only upon \textit{marginal means}: that is the column and row mean outcomes for each feature level averaging across all other features. A marginal mean describes the level of favorability toward profiles that have a particular feature level, ignoring all other features. For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities: a marginal mean of 0 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x) = 0$ while a marginal mean of 1 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x)=1$, where $Y$ is a binary outcome and $X$ is a vector of profile features.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany). Instead, the marginal mean can range from the probability of co-occurrence to 1 minus that probability. If there are five levels of a feature, each shown with equal probability, then the probability of co-occurrence is $\frac{1}{5}*\frac{1}{5} = 0.04$ such that the marginal mean can take values in the range $(0.04,0.96)$. If the design is constrained so that features cannot be the same for both immigrants, then the marginal means fully range from zero to one. This constraint on the range of the marginal means also constrains the range of AMCEs. Notably, many conjoints provide features with only two levels, such as the male-versus-female candidate feature examined by \citet{TeeleKallaRosenbluth2018} or \citet{HainmuellerHopkinsYamamoto2014} in their conjoints on candidate choice. In such cases, the probability of co-occurrence is $\frac{1}{2}*\frac{1}{2} = 0.25$ bounding the AMCE for female (as opposed to male) candidates to the range $(-0.5, 0.5)$ if both candidates can have the same sex. Caution is therefore needed in comparing the relative size of features with few levels to features with many levels given that effects have different bounds.} With rating scale outcomes, marginal means can vary arbitrarily along the outcome scale used.

@@

\noindent These examples make clear that despite the \textit{causal} inference potentially provided by the AMCE, the quantity of interest is frequently used to provide a characterization of a preferences that has a distinctly descriptive flavor about the relative \textit{levels} of support across profiles and also across subgroups of respondents. Indeed, this style of description is widespread in conjoint analyses. This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature. A positive (negative) AMCE is read as higher (lower) favorability but it is only higher (lower) relative to whatever category serves as the baseline. For example, in the \citeauthor{HainmuellerHopkinsYamamoto2014} candidate example, choosing a non-religious candidate as a baseline means the AMCEs in the candidate experiment are all expressed relative to this non-religious baseline; the difference (if any) between other pairs of marginal means (e.g., evaluations of Mormon and Evangelical candidates) is not obvious. Relatedly, the negative direction (and the size) of the AMCEs for Mormon and Evangelical candidates would be different if the least-liked category (Mormon candidates) were the reference group. In that case, the AMCE for Evangelicals would be small and positive and the AMCEs for all other categories (including the presented reference category, ``none'') would be large and positive. More trivially, \citet{TeeleKallaRosenbluth2018} describe their comparisons about public preferences for female candidates relative to male candidates, but could have equivalent described patterns of equal size but opposite sign comparing preferences over male relative to female candidates.

@@

@@

Given the need to choose a reference category for every feature in order to estimate AMCEs, an important question is: how do researchers decide which of tens of thousands of possible experimental cells should be selected as the reference category? Examining recently published conjoint analyses, it appears that the choice of reference category is either arbitrary or based upon substantive intuition about the meaning of feature levels. For example, \citet{HainmuellerHopkinsYamamoto2014} choose female immigrants as a baseline in their immigration experiment, thus providing an estimate of the AMCE of being male, while \citet{TeeleKallaRosenbluth2018} choose male candidates as a baseline in their conjoint, thus providing an estimate of the AMCE of being female. The choice is seemingly innocuous. Sometimes choices of reference category appear to be driven by substantive knowledge: on language skills of immigrants in their immigration experiment, \citet{HainmuellerHopkinsYamamoto2014} choose fluency as a baseline; on the prior trips to the US feature, ``never'' is chosen as the baseline.

@@

While seemingly arbitrary and innocuous, the choice of reference category can provide highly distorted descriptive interpretations of preferences among subgroups of respondents. This occurs when researchers examine \textit{conditional} AMCEs, wherein AMCEs are calculated separately for subgroups of respondents and those conditional estimates are directly compared \citep[13]{HainmuellerHopkinsYamamoto2014}. Conditional AMCEs convey the causal effect of an experimental factor on overall favorability among the subgroup of interest. Consider, for example, a two-condition candidate choice experiment where Democratic and Republican respondents are exposed to either a male or female candidate and opinions toward the candidate serve as the outcome. It is sensible to imagine that effects of candidate sex might differ for the two groups and therefore to compare the size of treatment between the two groups. Perhaps Democrats are more responsive to candidate sex than are Republicans, making the causal effect larger for Democrats than Republicans. When conjoint analysts engage in subgroup comparisons, they are engaging in this kind of search for heterogeneous treatment effects across subgroups, but across a much larger number of experimental factors.

Discussions of conditional AMCEs in conjoint analyses often explicitly or implicitly engage in this kind of discussion comparing the size and direction of subgroup causal effects. Indeed, Table \ref{tab:papers} reports a list of recently published articles in political science that engage in this form of subgroup analysis. Given the common practice of descriptively interpreting conjoint experimental results, such subgroup analyses seem perfectly intuitive and the set of subgroups listed in the last column of Table \ref{tab:papers} contains some unsurprising covariates, such as partisanship, that are of obvious theoretical interest in almost any study of individual preferences. If interpreted as a difference in the size of the \textit{causal effect} for two groups, such comparisons are perfectly consistent with more traditional experimental analysis and a perfectly acceptable interpretation of the conjoint results.

@@

Yet, just as analysis of full sample conjoint data is often descriptive in nature, so too do conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally. For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} visually compare the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22). \citet{BallardRosaMartinScheve2016} make similar comparisons in their tax policy conjoint: ``While there are few strong differences in preferences for taxing the lower three income groups (the `hard work' group has slightly lower elasticities for taxing the poor), there are strong differences in preferences for taxing the rich'' (12). In \citet{BechtelScheve2013} conjoint on support for international climate change agreements in the United States, United Kingdom, Germany, and France, they summarize their results as ``We find that individuals in all four countries largely agree on which dimensions are important and to what extent'' (13765). In these examples, the differences between conditional AMCEs are used as a way of descriptively characterizing differences in \textit{preferences} (i.e. levels of support) between the groups rather than differences in \textit{causal effects on preferences} in the groups.

The selection of a reference category, while earlier an innocuous analytic decisions, becomes substantially consequential for this kind descriptive reading of conditional AMCEs. Most obviously, using AMCEs descriptively prevents analysts from describing levels of favorability in the reference category but also can lead to misinterpretations of patterns in preferences. AMCEs are relative, not absolute, statements about preferences. As such, there is simply no predictable connection between subgroup causal effects and the levels of underlying subgroup preferences. Yet analysts and their readers frequently interpret differences in conditional AMCEs as differences in underlying preferences. While AMCEs do provide insight into the descriptive variation in preferences within-group and across-features, and conditional AMCEs do estimate the size of causal effects of features within groups, AMCEs cannot provide direct insight into the pattern of preferences between groups because they do not provide information about \textit{absolute} levels of favorability toward profiles with each feature (or combination of features).

@@

\noindent The effect of $x$ when $z=0$ is given by $\beta_1$. The effect of $x$ when $z=1$ is given by $\beta_3$. These are, in essence, the conditional AMCEs in a conjoint analysis. Yet the difference in AMCEs ($\beta_3 - \beta_1$) is not equal to the difference in preferences between the two groups, which is $\bar{y}_{z=1|x=1} - \bar{y}_{z=0|x=1}$ (estimated by $(\beta_2 + \beta_3) - (\beta_0 + \beta_1)$). The difference-in-AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$. Yet the standard AMCE-centric conjoint analysis does not present or characterize absolute favorability in the reference category. Similarity of conditional AMCEs only means similarity of the \textit{causal effect} of the feature across groups, not similarity of \textit{preferences} unless preferences toward profiles with the reference category are equivalent in both groups. Given the reference category choice is typically arbitrary or driven by substantive knowledge of the levels, there is never any reason to expect that an arbitrarily selected reference category satisfies this equality requirement. When using a difference-in-AMCEs comparison to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.

>>>>

{\abstract Conjoint analysis is now a common tool for studying political preferences. The method disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as political candidates or public policies. Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs). These measure the degree to which a given value of a conjoint profile feature increases, or decreases, people’s support for the overall profile relative to a baseline, averaging across all respondents and all other profile features. While the AMCE has a clear causal interpretation (about the \textit{effect} of features), most published conjoint analyses also use AMCEs to describe \textit{levels} of preferences or favorability. This often means comparing AMCEs among subgroups of respondents. We show that using conditional AMCEs to describe the degree of agreement among subgroups can be misleading as regression interactions are sensitive to the reference category used in the analysis. This leads to inferences about subgroup differences in preferences that have arbitrary sign, size, and significance. We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation using two quantities of interest: the marginal mean and the omnibus F-test. Given the accelerating use of conjoint analyses in political science, we offer advice for best practice in the analysis and presentation of conjoint experiments.}

@@

One aspect of the dramatic increase in the use of experiments within political science \citep{Druckmanetal2006, Mutz2011} is the establishment of conjoint experimental designs as a prominent methodological tool. While survey experiments have traditionally examined just one or two factors that might shape outcomes \citep[see, for reviews,][]{GainesKuklinskiQuirk2007, Sniderman2011}, conjoint designs allow researchers to study the independent effects on preferences of many features of complex, multidimensional objects. These include many different types of phenomena, such as political candidates \citep{Campbelletal2016, TeeleKallaRosenbluth2018}, immigrant admissions \citep{HainmuellerHopkins2015, BansakHainmuellerHangartner2016, WrightLevyCitrin2016}, and public policies \citep{GallegoMarx2017, Hankinson2018}. Factorial designs of this sort have a long history, but the driving force behind this use of conjoint analysis has been the introduction by \citet{HainmuellerHopkinsYamamoto2014} of a small-sample, fully randomized conjoint design. The associated analytic approach emphasizes a single quantity of interest: the average marginal component effect (AMCE). By capturing the multidimensionality of target objects, the randomized conjoint design breaks any explicit, or implicit, confounding between features of these objects. This gives the AMCE a clear causal interpretation: the degree to which a given value of a feature increases, or decreases, respondents' favorability towards a packaged conjoint profile relative to a baseline.

While randomization of profile features gives the AMCE a causal interpretation, most published conjoint analyses in political science use AMCEs not only for \textit{causal} purposes (interpreting AMCEs as effect sizes), but also for \textit{descriptive} purposes. The aim is to map levels of favorability toward a multidimensional object across its various features.\footnote{See \citet{Shmueli2010} for an elaboration on the distinctions between explanatory (causal) modelling, descriptive modelling, and predictive modelling.} In this sense, conjoints are often applied like list experiments, using randomization to measure a sample's preferences over something difficult to measure with direct questioning. A positive AMCE for a given feature can be read as a descriptive measure of high favorability towards profiles with that feature. The quantity is causal, but it is often read descriptively.

This is particularly the case for subgroup analyses of conjoint experiments. Such exercises are an increasingly common feature of experimental analysis \citep{GreenKern2012, RatkovicTingley2017, GrimmerMessingWestwood2017, EgamiImai2018}. For example, the \citet{HainmuellerHopkinsYamamoto2014} study of immigration attitudes splits the sample in two using a measure of ethnocentrism and then compares AMCEs for the two subgroups. Similarly, \citet{BansakHainmuellerHangartner2016} compare preferences toward immigrants across number of binary respondent characteristics: age, education, left-right ideology, and income. Other examples abound. \citet{BallardRosaMartinScheve2016} compare preferences over tax policies across a number of subgroups defined by demographics and political orientations; \citet{BechtelScheve2013} compare AMCEs on climate agreements across four different countries, and across subgroups of respondents; and \citet{TeeleKallaRosenbluth2018} compare AMCEs for features of male and female political candidates among male and female respondents. Most of these comparisons are visual or informal. But some involve explicit estimation of the subgroup difference, such as when \citet{KirklandCoppock2017} compare conditional AMCEs across hypothetical partisan and nonpartisan elections. Interpretation of subgroup AMCEs thus involves an implied quantity of interest: the \textit{difference} between two conditional AMCEs.

What is not necessarily obvious in such analyses is that differences-in-preferences (that is to say, the difference in degree of favorability toward profiles containing a given feature) are not directly reflected in subgroup differences-in-AMCEs. A difference in effect sizes is distinct from a difference in preferences. We show that a difference in two (or more) subgroups' favorability toward a conjoint feature --- like a difference in willingness to support a particular type of immigrant between high and low ethnocentrism respondents --- is only rarely reflected in the difference-in-AMCEs. In fact, no information about the similarity of the subgroups' preferences is provided by comparisons of subgroup AMCEs, yet such comparisons are commonly made in practice.

As we will show, where preferences in subgroups toward the experimental reference category are similar, the difference-in-AMCEs conveys preferences reasonably well. The problem occurs when preferences between subgroups diverge in the reference category. Here, the difference-in-AMCEs is a misleading representation of underlying patterns of favorability. Given most published conjoint studies report results based upon reference categories chosen for \textit{substantive} reasons about the nature or meaning of the levels rather than the configuration of preferences revealed in the experiment, difference-in-AMCEs should not be assumed to be interpretable as differences in subgroup preferences. The root of this error is likely familiar to many researchers: it is simply a matter of regression specification for models involving interactions between categorical regressors. \citet{EgamiImai2018}, for example, provide an extensive discussion of the implications of this property for interpreting causal interactions between randomized features of conjoint profiles. The state of the published literature would suggest the problem remains non-obvious when applied to descriptive analysis of subgroups in conjoint designs.

In what follows, we demonstrate the challenges of conjoint analysis and remind readers of how reference category choice for profile features creates problems for comparing conditional AMCEs across respondent subgroups. We show how the use of an arbitrary reference category means the size, direction, and statistical significance of differences-in-AMCEs have little relationship to the underlying degree of favorability of the subgroups toward profiles with particular features. Reference category choices can make similar preferences look dissimilar and dissimilar preferences look similar. We demonstrate this with examples drawn from the published political science literature (namely experiments by \citealt{HainmuellerHopkinsYamamoto2014, BechtelScheve2013, TeeleKallaRosenbluth2018}). The paper then provides suggestions for improved conjoint reporting and interpretation based around two quantities of interest drawn from the factorial experimentation literature: (a) unadjusted marginal means, a quantity measuring favorability toward a given feature, and (b) an omnibus F-test, measuring differences therein. Software for the R programming language to support our findings --- and that can be used to examine sensitivity of conjoint analysis to reference category selection, calculate AMCEs and marginal means, perform subgroup analyses, and test for subgroup differences in any conjoint experiment --- is demonstrated throughout. We conclude with advice for best practices in the analysis and presentation of conjoint results.

@@

Analytically, a fully randomized conjoint design without constraints between profile features is simply a full-factorial experiment (with some cells possibly, albeit randomly, left unobserved). All quantities of interest relevant to the analysis of conjoint designs therefore derive from combinations of cell means, marginal means, and the grand mean, as in the traditional analysis of factorial experiments. In a forced choice conjoint design, the \textit{grand mean} is by definition 0.5 (i.e., 50\% of all profiles shown are chosen and 50\% are not chosen). \textit{Cell means} are the mean outcome for each particular combination of feature levels. In the full-factorial design discussed by \citet{HainmuellerHopkinsYamamoto2014} and now widely used in political science, many or perhaps most cell means are unobserved. For example, in their candidate choice experiment, there are $2*6*6*6*2*6*6*6 = 186,624$ cell means, but only 3,466 observations. About 98\% of cell means are unobserved. While this would be problematic for attempting to infer pairwise comparisons between cells, conjoint analysts mostly focus on the marginal effects of each feature rather than more complex interactions. Appendix \ref{app:quantities} provides detailed notation and elaborations of these definitions of quantities of interest.

In fully randomized designs, the average marginal component effects (AMCEs) are simply marginal effects of changing one feature level to another, all else constant. AMCEs therefore depend only upon \textit{marginal means}: that is the column and row mean outcomes for each feature level averaging across all other features. A marginal mean describes the level of favorability toward profiles that have a particular feature level, ignoring all other features. For example, in the common forced-choice design with two alternatives, marginal means have a direct interpretation as probabilities. A marginal mean of 0 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x) = 0$. While a marginal mean of 1 indicates respondents select profiles with that feature level with probability $P(Y=1|X=x)=1$, where $Y$ is a binary outcome and $X$ is a vector of profile features.\footnote{It is not possible for the marginal mean to equal zero or one if pairs of profiles shown together are allowed to have the same level of a given feature (for example, both immigrants are from Germany). Instead, the marginal mean can range from the probability of co-occurrence to 1 minus that probability. If there are five levels of a feature, each shown with equal probability, then the probability of co-occurrence is $\frac{1}{5}*\frac{1}{5} = 0.04$ such that the marginal mean can take values in the range $(0.04,0.96)$. If the design is constrained so that features cannot be the same for both immigrants, then the marginal means fully range from zero to one. This constraint on the range of the marginal means also constrains the range of AMCEs. Notably, many conjoints provide features with only two levels, such as the male-versus-female candidate feature examined by \citet{TeeleKallaRosenbluth2018} or \citet{HainmuellerHopkinsYamamoto2014} in their conjoints on candidate choice. In such cases, the probability of co-occurrence is $\frac{1}{2}*\frac{1}{2} = 0.25$ bounding the AMCE for female (as opposed to male) candidates to the range $(-0.5, 0.5)$ if both candidates can have the same sex. Caution is therefore needed in comparing the relative size of features with few levels to features with many levels given that effects have different bounds.} With rating scale outcomes, marginal means can vary arbitrarily along the outcome scale used.

@@

\noindent These examples make clear that despite the \textit{causal} inference potentially provided by the AMCE, the quantity of interest is frequently used to provide a characterization of a preferences that has a distinctly descriptive flavor about the relative \textit{levels} of support across profiles and also across subgroups of respondents. Indeed, this style of description is widespread in conjoint analyses. This use of conjoints to provide descriptive inferences about patterns of preferences is important because AMCEs are defined as \textit{relative} quantities, requiring that patterns of preferences are expressed against a baseline, reference category for each conjoint feature. A positive AMCE is read as higher favorability but it is only higher relative to whatever category serves as the baseline. For example, in the \citeauthor{HainmuellerHopkinsYamamoto2014} candidate example, choosing a non-religious candidate as a baseline and interpreting the resulting AMCES means that the differences between other pairs of marginal means (e.g., evaluations of Mormon and Evangelical candidates) are not obvious. The negative direction, and the size, of the AMCEs for Mormon and Evangelical candidates would be different if the least-liked category of Mormons were the reference group. More trivially, \citet{TeeleKallaRosenbluth2018} describe their comparisons about public preferences for female candidates relative to male candidates, but could have equivalent described patterns of equal size but opposite sign comparing preferences over male relative to female candidates.

@@

% DECIDE WHETHER TO KEEP THIS (AND FIGURE 2):

@@

How do researchers decide which of tens of thousands of possible experimental cells should be selected as the reference category? Examining recently published conjoint analyses, it appears that the choice of reference category is either arbitrary or based upon substantive intuition about the meaning of feature levels. For example, \citet{HainmuellerHopkinsYamamoto2014} choose female immigrants as a baseline in their immigration experiment, thus providing an estimate of the AMCE of being male, while \citet{TeeleKallaRosenbluth2018} choose male candidates as a baseline in their conjoint, thus providing an estimate of the AMCE of being female. The choice is seemingly innocuous. Sometimes choices of reference category appear to be driven by substantive knowledge: on language skills of immigrants in their immigration experiment, \citet{HainmuellerHopkinsYamamoto2014} choose fluency as a baseline; on the prior trips to the US feature, ``never'' is chosen as the baseline.

@@

While seemingly arbitrary and innocuous, the choice of reference category can provide highly distorted descriptive interpretations of preferences among subgroups of respondents. This occurs when researchers examine \textit{conditional} AMCEs, wherein AMCEs are calculated separately for subgroups of respondents and those conditional estimates are directly compared \citep[13]{HainmuellerHopkinsYamamoto2014}. Conditional AMCEs convey the causal effect of an experimental factor on overall favorability among the subgroup of interest. Consider, for example, a two-condition candidate choice experiment where Democratic and Republican respondents are exposed to either a male or female candidate and opinions toward the candidate serve as the outcome. It is reasonable to imagine that effects of candidate sex might differ for the two groups and therefore to compare the size of treatment between the two groups. Perhaps Democrats are more responsive to candidate sex than are Republicans, making the causal effect larger for Democrats than Republicans. When conjoint analysts engage in subgroup comparisons, they are engaging in this kind of search for heterogeneous treatment effects across subgroups, but across a much larger number of experimental factors.

As Table \ref{tab:papers} shows, discussions of conditional AMCEs in conjoint analyses often compare the size, and direction, of subgroup causal effects. Given the common practice of descriptively interpreting conjoint experimental results, such subgroup analyses seem perfectly intuitive. The set of subgroups listed in the last column of Table \ref{tab:papers} contains some unsurprising covariates, such as partisanship, that are of obvious theoretical interest in almost any study of individual preferences. If interpreted as a difference in the size of the \textit{causal effect} for two groups, such comparisons are perfectly consistent with more traditional experimental analysis and a perfectly acceptable interpretation of the conjoint results.

@@

Yet, just as analysis of full sample conjoint data is often descriptive in nature, it is also the case that conjoint analysts frequently interpret differences in conditional AMCEs descriptively rather than causally. For example, in one analysis \citet{HainmuellerHopkinsYamamoto2014} visually compare the pattern of AMCEs among high- and low-ethnocentrism respondents and interpret that ``the patterns of support are generally similar for respondents irrespective of their level of ethnocentrism'' (22). \citet{BallardRosaMartinScheve2016} make similar comparisons in their tax policy conjoint: ``While there are few strong differences in preferences for taxing the lower three income groups (the `hard work' group has slightly lower elasticities for taxing the poor), there are strong differences in preferences for taxing the rich'' (12). In \citet{BechtelScheve2013} conjoint on support for international climate change agreements in the United States, United Kingdom, Germany, and France, they summarize their results as ``We find that individuals in all four countries largely agree on which dimensions are important and to what extent'' (13765). In these examples, the differences between conditional AMCEs are used as a way of descriptively characterizing differences in \textit{preferences} (i.e. levels of support) between the groups rather than differences in \textit{causal effects on preferences} in the groups.

The selection of a reference category, while earlier an innocuous analytic decision, becomes substantially consequential for a descriptive reading of conditional AMCEs. Most obviously, using AMCEs descriptively prevents any description of the levels of favorability in the reference category. It can also lead to misinterpretations of patterns in preferences. AMCEs are relative, not absolute, statements about preferences. As such, there is simply no predictable connection between subgroup causal effects and the levels of underlying subgroup preferences. Yet analysts and their readers frequently interpret differences in conditional AMCEs as differences in underlying preferences. AMCEs do provide insight into the descriptive variation in preferences within-group and across-features, and conditional AMCEs do estimate the size of causal effects of features within groups. But AMCEs cannot provide direct insight into the pattern of preferences between groups because they do not provide information about \textit{absolute} levels of favorability toward profiles with each feature (or combination of features).

@@

\noindent The effect of $x$ when $z=0$ is given by $\beta_1$. The effect of $x$ when $z=1$ is given by $\beta_3$. These are, in essence, the conditional AMCEs in a conjoint analysis. Yet the difference in AMCEs ($\beta_3 - \beta_1$) is not equal to the difference in preferences between the two groups, which is $\bar{y}_{z=1|x=1} - \bar{y}_{z=0|x=1}$ (estimated by $(\beta_2 + \beta_3) - (\beta_0 + \beta_1)$). The difference-in-AMCEs only equals the difference in preferences when $\beta_2 \equiv \beta_0$. Yet the standard AMCE-centric conjoint analysis does not present absolute favorability in the reference category. Similarity of conditional AMCEs only means similarity of the \textit{causal effect} of the feature across groups, not similarity of \textit{preferences} unless preferences toward profiles with the reference category are equivalent in both groups. Given the reference category choice is typically arbitrary or driven by substantive knowledge of the levels, there is never any reason to expect that the reference category satisfies this equality requirement. When using a difference-in-AMCEs comparison to estimate a difference in preferences, the size and direction of the bias is determined by the size of the difference in preferences toward the reference category within each subgroup.

To draw this example out more fully, the upper panel of Figure \ref{fig:tkr_replication} shows AMCEs for \citeauthor{TeeleKallaRosenbluth2018}'s candidate choice experiment for the full sample of respondents. The second panel shows full sample marginal means. Respondents' preference for female candidates is very apparent in both forms of analysis in the upper two panels because the AMCE definitionally equals the difference in marginal means. But how do Republicans and Democrats differ in their preferences over male and female candidates? The third panel shows conditional AMCEs separately for Democratic and Republican voters, as provided in the original paper and the lower panel shows the results using conditional marginal means for Democratic and Republican voters.\footnote{We opt here for visual presentation of results; tabular presentation of AMCEs, marginal means, and associated standard errors for all examples are included in the Appendix.} By requiring a reference category fixed to zero, the conditional AMCE results in the third panel suggest that there is a very large difference in favorability toward female candidates between Republican and Democratic respondents. In reality, however, the difference in these conditional AMCEs (0.086) reflects the true difference in favorability toward female candidates (difference: 0.045; Democrats: 0.537, Republicans: 0.492) \textit{plus} the difference in favorability toward male candidates (difference: 0.045; Democrats: 0.463, Republicans: 0.508). Because Democrats and Republicans actually differ in their views of profiles containing the reference (male) category, AMCEs sum the true differences in preferences for a given feature level with the difference in preferences toward the reference category.\footnote{Another example that clearly demonstrates the discrepancy between the differences in preferences and the differences in conditional AMCEs can be seen very clearly in the ``political experience'' feature of this experiment (see Supporting Materials). The conditional AMCEs correctly convey that both Democrats and Republicans are more likely to favor experienced than inexperienced candidates. Reading the AMCEs descriptively, however, would suggest that Democratic voters are more favorable toward candidates with all levels of experience compared to Republican voters (i.e., Republicans and Democrats differ in their preferences over experienced candidates). In reality, however, the conditional marginal means reveal that actually Democrats and Republicans have very similar preferences toward candidates with 1 or 3 years of experience, but differ dramatically in their preferences over candidates with no experience (the reference category) and those with 8 years experience. Democrats are much more sensitive to experience than are Republicans and important differences in preferences between the groups are apparent for very high and very low experience, but the conditional AMCEs suggest that preferences differ at all levels of experience, when in reality they do not.}
